### 2017-02-23 MSSM/MSSM.tex
Adding combined model interpretations

Interpretations in MSSM benchmark scenarios to be added.

>>>>

Figure \ref{fig:mssm_mhmodp_20152016}a shows the exclusion obtained in the $m_{\PHiggslight}^{\text{mod+}}$ 
scenario by combining the 2015 and 2016 analyses. Figure \ref{fig:mssm_mhmodp_20152016}b shows this exclusion
in the hMSSM scenario. On both figures the expected and observed exclusion from the
2016 analysis only are overlaid, which shows how the combination increases the
size of the excluded area. In the hMSSM scenario the feature already visible in figure \ref{fig:mssm_mhmodp_2016}b
has grown by combining the two datasets. Future analyses using even more data will be able to fully close
the gap between the two excluded regions.

\begin{figure}[h!]
\begin{center}
\subfloat[$m_{\PHiggslight}^{\text{mod}+}$ scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_mhmodp_cmb.pdf}}~\\
\subfloat[hMSSM scenario]{\includegraphics[width=0.6\textwidth]{./MSSM/Figures/mssm_combination_hMSSM_cmb.pdf}}
\end{center}
\caption[Exclusion in the $m_{\PHiggslight}^{\text{mod+}}$ scenario and the hMSSM
scenario of the combination of the 2015 and 2016 \AHtotautau analyses.]{Exclusion in (a) the $m_{\PHiggslight}^{\text{mod}+}$ scenario and (b) the hMSSM scenario 
obtained by the combination
of all channels of the 2015 and 2016 \AHtotautau analyses. The blue shaded area bounded by the 
solid black line is the observed exclusion, with the dashed black line the
expected exclusion. The light and dark grey bands indicate
the $\pm 1\sigma$ (68\%) and $\pm 2\sigma$ (95\%) probability intervals on the expected limit.
The red shaded area in the $m_{\PHiggslight}^{\text{mod}+}$ figure
is excluded by the lack of a light Higgs boson with mass compatible with $125\,\GeV$. The dashed (solid)
blue lines indicate the expected (observed) exclusion from the 2016 analysis alone.}
\label{fig:mssm_mhmodp_20152016}
\end{figure}
